The Inner Mass-Ratio Distribution of Intermediate-Mass Stars

### 2016-01-27 paper/ms.tex
Used new aasjournal references style.

%\documentclass[12pt,preprint]{aastex}
\documentclass{emulateapj}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{url}
\usepackage{bm}
\bibliographystyle{astroads}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
\renewcommand{\vec}[1]{\bm{#1}}
\DeclareMathOperator\erf{erf}
\begin{document}

@@

Beyond the overall multiplicity rate, the mass ratio, period, and eccentricity distributions of a binary star population place important constraints on the mode of binary star formation. Most binary stars are thought to form via core fragmentation \citep{Boss1979, Boss1986, Bate1995}, in which a collapsing core fragments into two or more individual protostars. The number and initial masses of the fragments are set by the total core mass, as well as its rotation, turbulence, and its temperature and density structure. If the fragments are separated by $\gtrsim 1000$ AU, they will evolve relatively independently of each other, accreting mass from the core material onto their own protostellar disks and then onto the protostars themselves. However close fragments ($a \sim 100$ AU) will interact with each other; the protostellar disk may be truncated, destabilized, or even merge into a circumbinary disk if the separation is small enough. In addition, unstable disk can fragment to form low-mass companions \citep{Kratter2006, Stammatellos2011}. The mass ratios of close companions formed via either mechanism should be effected by preferential accretion. Most work has suggested that the disk material will preferentially accrete onto the lower mass companion \citep{Bate1997, BBB2002}; however, recent work has indicated that magnetic disk braking may result in preferential accretion onto the more massive component \citep{Zhao2013} instead. In either case, we would expect to find a different mass ratio distribution for companions inside a few $100$ AU and companions on wider orbits.

@@

\begin{itemize}
\item $k_C = 0.646$ day/Myr
\item $k_I = 452$ Myr/day
\end{itemize}
We estimate the convective timescale ($\tau$) by interpolating Table 1 of \citet{Barnes2010}. We then sample the system age $t$ (see Section \ref{sec:sp} and Table \ref{tab:primary}), and sample the initial rotation period $P_0$ as log-uniform from 0.2 to 10 days. Equation \ref{eqn:gyro} then gives a current rotation period for each sample, which we convert to an equatorial velocity with the stellar radius $R$. We estimate the stellar radius by interpolating Dartmouth pre main sequence isochrones [CITE] using the temperature temperature and age. TODO: Probably need to rewrite at least parts of this...

>>>>

%\documentclass[12pt,preprint]{aastex}
\documentclass{emulateapj}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{url}
\usepackage{bm}
\bibliographystyle{aasjournal}
\providecommand{\e}[1]{\ensuremath{\times 10^{#1}}}
\renewcommand{\vec}[1]{\bm{#1}}
\DeclareMathOperator\erf{erf}
\begin{document}

@@

Beyond the overall multiplicity rate, the mass ratio, period, and eccentricity distributions of a binary star population place important constraints on the mode of binary star formation. Most binary stars are thought to form via core fragmentation \citep{Boss1979, Boss1986, Bate1995}, in which a collapsing core fragments into two or more individual protostars. The number and initial masses of the fragments are set by the total core mass, as well as its rotation, turbulence, and its temperature and density structure. If the fragments are separated by $\gtrsim 1000$ AU, they will evolve relatively independently of each other, accreting mass from the core material onto their own protostellar disks and then onto the protostars themselves. However close fragments ($a \sim 100$ AU) will interact with each other; the protostellar disk may be truncated, destabilized, or even merge into a circumbinary disk if the separation is small enough. In addition, unstable disk can fragment to form low-mass companions \citep{Kratter2006, Stamatellos2011}. The mass ratios of close companions formed via either mechanism should be effected by preferential accretion. Most work has suggested that the disk material will preferentially accrete onto the lower mass companion \citep{Bate1997, BBB2002}; however, recent work has indicated that magnetic disk braking may result in preferential accretion onto the more massive component \citep{Zhao2013} instead. In either case, we would expect to find a different mass ratio distribution for companions inside a few $100$ AU and companions on wider orbits.

@@

\begin{itemize}
\item $k_C = 0.646$ day/Myr
\item $k_I = 452$ Myr/day
\end{itemize}
We estimate the convective timescale ($\tau$) by interpolating Table 1 of \citet{Barnes2010a}. We then sample the system age $t$ (see Section \ref{sec:sp} and Table \ref{tab:primary}), and sample the initial rotation period $P_0$ as log-uniform from 0.2 to 10 days. Equation \ref{eqn:gyro} then gives a current rotation period for each sample, which we convert to an equatorial velocity with the stellar radius $R$. We estimate the stellar radius by interpolating Dartmouth pre main sequence isochrones [CITE] using the temperature temperature and age. TODO: Probably need to rewrite at least parts of this...
